Visualizing Project Evolution Through Abstract Syntax Tree Analysis

### 2016-07-04 paper/document.tex
Fix typos.

By adding interaction, the user is able to explore the timeline to find the specific information that they are interested in and drill-down at their leisure. Although our tool extracts a great deal of information, users can gradual reveal more information as they need it, rather than be bombarded with all of the information at once.

@@

To determine if type coverage yields different information than file coverage, we analyzed four open source Java projects: ANTLR4, Apache BookKeeper, Apache Curator and Apache Tika (Figure~\ref{tab:project-summary}). Three of the four projects were collected from the Apache foundation, as they host a large number of well-curated open source Java projects. We counted the file coverage and type coverage on a commit-by-commit basis for each author. That is, each datum represents a commit with three dimensions: file coverage, type coverage, and its commit date. Data is sorted in ascending order of commit date. Table~\ref{tab:summary} lists a summary of the statistics measured.

@@

In this paper, we introduced TypeV, a code repository analysis and visualization tool. Using commit-by-commit abstract syntax tree differencing enables insightful visualization that is not captured by tools that use commit counts, line counts, or file changes alone. In this paper, we addressed the following research questions:

>>>>

By adding interaction, the user is able to explore the timeline to find the specific information that they are interested in and drill-down at their leisure. Although our tool extracts a great deal of information, users can gradually reveal more information as they need it, rather than be bombarded with all of the information at once.

@@

To determine if type coverage yields different information than file coverage, we analyzed four open source Java projects: ANTLR4, Apache BookKeeper, Apache Curator and Apache Tika (Table~\ref{tab:project-summary}). Three of the four projects were collected from the Apache foundation, as they host a large number of well-curated open source Java projects. We counted the file coverage and type coverage on a commit-by-commit basis for each author. That is, each datum represents a commit with three dimensions: file coverage, type coverage, and its commit date. Data is sorted in ascending order of commit date. Table~\ref{tab:summary} lists a summary of the statistics measured.

@@

In this paper, we introduced TypeV, a code repository analysis and visualization tool. Using commit-by-commit abstract syntax tree differencing enables insightful visualizations that are not captured by tools that use commit counts, line counts, or file changes alone. In this paper, we addressed the following research questions:
